CMC_DataCleaning

### 2019-12-16 code/CMC_DataProcessing.Rmd
CMC version 2

## Pull CMC Data From Synapse and Prep for Imputation - 
This data is protected

@@

activityName = 'Processed GTEx Genotypes TWAS';
activityDescription = 'Proccessed and Filtered GTEx Genotype Data';

CODE <- syn_temp$store(synapseclient$Folder(name = "GTExGenotypes", parentId = parentId))
CODEalt <- syn_temp$store(synapseclient$Folder(name = "GTExPreProcess", parentId = parentId))

@@

ENRICH_OBJ <- syn_temp$store( synapseclient$File( path='REPLACE TEST VALUE', name = 'REPLACE TEST VALUE', parentId=CODE$properties$id ), used = Syns_Used, activityName = activityName, executed = thisFile, activityDescription = activityDescription)
syn_temp$setAnnotations(ENRICH_OBJ, annotations = Var.all.annotations)
```

>>>>

## Pull CMC Data From Synapse and Prep for Imputation - 
This data is protected, you wil be required to apply for access through PhsycEncode
```{bash Pull_WGS, results='hide', echo=TRUE, cache=TRUE}
CORES=`expr $(nproc) - 2`
#Pull Data with needed SNPS only and fiter GTEx for that SNP List
synapse get syn20835005
synapse get syn20835007
synapse get syn20834996
~/TWAS/bin/plink --threads $CORES --bfile All_CEU_ToTrainForTWAS --write-snplist

mkdir CMC_Genos
synapse get syn10537112 --recursive --downloadLocation CMC_Genos/

mkdir CMC_Filt_Genos
touch merge.txt
#Pull out Snps
for i in {1..22}
  do
    #--positions plink.snplist 
    bcftools norm --threads $CORES --rm-dup snps -Oz CMC_Genos/CMC_chr$i.dose.vcf.gz > CMC_Filt_Genos/Filt_CMC_chr$i.dose.vcf.gz
    vcftools --gzvcf CMC_Filt_Genos/Filt_CMC_chr$i.dose.vcf.gz --plink --out CMC_Filt_Genos/Init_Filtered_chr$i
    echo 'CMC_Filt_Genos/Init_Filtered_chr'$i'.ped CMC_Filt_Genos/Init_Filtered_chr'$i'.map' >> merge.txt
  done
grep -v 'chr1.ped' merge.txt > foo
mv foo merge.txt

#Merge Genotype
~/TWAS/bin/plink --threads $CORES --file CMC_Filt_Genos/Init_Filtered_chr1 --merge-list merge.txt --make-bed --out Merged_Initial_CMC_Geno

#Remove old Map/Ped Files
rm CMC_Filt_Genos/Init_Filtered_chr*.map
rm CMC_Filt_Genos/Init_Filtered_chr*.ped
```

### ReName the MSBB SNPS so the can be combined
```{python ReNamer_ONE, echo=F, results='hide',python.reticulate=T}
import sys
import os
import re

InFile = 'All_CEU_ToTrainForTWAS.bim'
InFileb = 'Merged_Initial_CMC_Geno.bim' #LDREF_FiltSNPs.bim

RS_IDs = {}
RS_Pos = {}

F1 = open(InFile)
for line in F1:
	LINE = line.rstrip('\r\n')
	lst = LINE.split('\t')
	RS_IDs[ ''.join([lst[0], '_', lst[3]]) ] = lst[1]
	RS_Pos[ ''.join([lst[0], '_', lst[3]]) ] = lst[2]
F1.close()

#Open Output
OUT = open( ''.join([ InFileb.replace(".bim", ""), 'Renamed.bim']), 'w' )

F1 = open(InFileb)
for line in F1:
	LINE = line.rstrip('\r\n')
	lst = LINE.split('\t')
	if( ''.join([ lst[0], "_", lst[3] ]) in RS_IDs):
		Name = RS_IDs[ ''.join([ lst[0], "_", lst[3] ])]
		Entry = '\t'.join([ lst[0], Name, lst[2], lst[3], lst[4], lst[5] ])
		print >>OUT, Entry
	else:
		print >>OUT, LINE

F1.close()
OUT.close()
```

## Pull Imputation SNPS - 
```{bash Pull_impute, results='hide', echo=TRUE, cache=TRUE}
CORES=`expr $(nproc) - 2`

mv Merged_Initial_CMC_GenoRenamed.bim Merged_Initial_CMC_Geno.bim
~/TWAS/bin/plink --threads $CORES --bfile Merged_Initial_CMC_Geno --extract plink.snplist --make-bed --out CMC_Genos_For_Impute

@@

activityName = 'Processed CMC Genotypes TWAS';
activityDescription = 'Proccessed and Filtered CMC Genotype Data';

CODE <- syn_temp$store(synapseclient$Folder(name = "CMC_FilteredGenotypes", parentId = parentId))
#CODEalt <- syn_temp$store(synapseclient$Folder(name = "CMC_FilteredGenotypes", parentId = parentId))

@@

ENRICH_OBJ <- syn_temp$store( synapseclient$File( path='CMC_Genos_For_Impute.bim', name = 'CMC Genotypes For Imputing exp BIM', parentId=CODE$properties$id ), used = Syns_Used, activityName = activityName, executed = thisFile, activityDescription = activityDescription)
syn_temp$setAnnotations(ENRICH_OBJ, annotations = Var.all.annotations)

ENRICH_OBJ <- syn_temp$store( synapseclient$File( path='CMC_Genos_For_Impute.fam', name = 'CMC Genotypes For Imputing exp FAM', parentId=CODE$properties$id ), used = Syns_Used, activityName = activityName, executed = thisFile, activityDescription = activityDescription)
syn_temp$setAnnotations(ENRICH_OBJ, annotations = Var.all.annotations)

ENRICH_OBJ <- syn_temp$store( synapseclient$File( path='CMC_Genos_For_Impute.bed', name = 'CMC Genotypes For Imputing exp BED ', parentId=CODE$properties$id ), used = Syns_Used, activityName = activityName, executed = thisFile, activityDescription = activityDescription)
syn_temp$setAnnotations(ENRICH_OBJ, annotations = Var.all.annotations)
```

## Clean

```{bash Pull_WGS, results='hide', echo=TRUE, cache=TRUE}
rm *.fam
rm *.bed
rm *.bim
rm *.fam
rm *.nosex
rm *.ped
rm *.map
rm *.missnp
rm *.log
rm *.snplist
rm merge.txt
rm -r CMC_Genos/
rm -r CMC_Filt_Genos/
```
